\subsection{Cellulose degrader DNA shifts further along the BD gradient upon
$^{13}$C incorporation than xylose degrader DNA} 
Cellulose responders exhibited a greater shift in BD than xylose responders in
response to isotope incorporation (Figure~\ref{fig:shift}, p-value
1.86e$^{-06}$). $^{13}$C-cellulose responders shifted on average 0.0163 g/mL
(sd 0.0094) whereas xylose responders shifted on average 0.0097 (sd
0.0094). For reference, 100\% $^{13}$C DNA shifts X.XX g/mL
relative to the BD of its $^{12}$C counterpart. DNA BD increases
as its ratio of $^{13}$C to $^{12}$C increases. An organism that only
assimilates C into DNA from a $^{13}$C isotopically labeled source, will have a
greater $^{13}$C:$^{12}$C ratio in its DNA than an organism utilizing a mixture
of isotopically labeled and unlabeled C sources. Upon labeling, DNA from an
organism that incorporates exclusively $^{13}$C will increase in buoyant density
more than DNA from an organism that does not exclusively utilize
isotopically labeled C. Therefore the magnitude DNA buoyant density shifts
indicate substrate specificity given our experimental design as only one
substrate was labeled in each amendment. We measured density shift
as the change in an OTU's density profile center of mass between corresponding
contol and labeled gradients. Density shifts, however, should not be evaluated
on an individual OTU basis as a small number of density shifts are observed for
each OTU and the variance of the density shift metric at the level of
individual OTUs is unknown. It is therefore more informative to compare density
shifts among substrate responder groups. Further, density shifts are based on
relative abundance profiles and would be theoretically muted in comparison to
density shifts based on absolute abundance profiles and should be interpreted
with this transformation in mind. It should also be noted that there was
overlap in observed density shifts between $^{13}$C-cellulose and
$^{13}$C-xylose responder groups suggesting that although cellulose degraders
are generally more substrate specific than xylose utilizers, some cellulose
degraders show less substrate specificity for cellulose than some xylose
utilizers for xylose (Figure~\ref{fig:shift}), and, each responder group
exhibits a range of substrate specificites (Figure~\ref{fig:shift}).