\thispagestyle{empty}
\newgeometry{tmargin=2cm, bmargin=2cm, lmargin=0.25cm, rmargin=0.25cm} 

\begin{longtable}{lrrP{5cm}rP{5cm}}

\caption{$^{13}$C-cellulose responders BLAST against Living Tree Project} \label{tab:cell} \\
\toprule 
    \textbf{OTU ID} & \textbf{Fold change} & \textbf{Day} & \textbf{Top BLAST hits} & \textbf{BLAST \%ID} & \textbf{Phylum;Class;Order} \\
\midrule
\endfirsthead

\multicolumn{3}{c}
{{\tablename\ \thetable{} -- continued from previous page}} \\
\midrule
    \textbf{OTU ID} & \textbf{Fold change} & \textbf{Day} & \textbf{Top BLAST hits} & \textbf{BLAST \%ID} & \textbf{Phylum;Class;Order} \\
\midrule
\endhead
    OTU.4446 & 3.49 & 7 & \mbox{\textit{Catenuloplanes niger}}, \mbox{\textit{Catenuloplanes castaneus}}, \mbox{\textit{Catenuloplanes atrovinosus}}, \mbox{\textit{Catenuloplanes crispus}}, \mbox{\textit{Catenuloplanes nepalensis}}, \mbox{\textit{Catenuloplanes japonicus}} & 97.72 & \mbox{\textit{Actinobacteria}} \mbox{\textit{Frankiales}} \mbox{\textit{Nakamurellaceae}} \\ \midrule
OTU.62 & 2.57 & 7 & \mbox{\textit{Nakamurella flavida}} & 100.0 & \mbox{\textit{Actinobacteria}} \mbox{\textit{Frankiales}} \mbox{\textit{Nakamurellaceae}} \\ \midrule
OTU.24 & 2.81 & 7 & \mbox{\textit{Cellulomonas aerilata}}, \mbox{\textit{Cellulomonas humilata}}, \mbox{\textit{Cellulomonas terrae}}, \mbox{\textit{Cellulomonas soli}}, \mbox{\textit{Cellulomonas xylanilytica}} & 100.0 & \mbox{\textit{Actinobacteria}} \mbox{\textit{Micrococcales}} \mbox{\textit{Cellulomonadaceae}} \\ \midrule
OTU.4 & 2.84 & 7 & \mbox{\textit{Agromyces ramosus}} & 100.0 & \mbox{\textit{Actinobacteria}} \mbox{\textit{Micrococcales}} \mbox{\textit{Microbacteriaceae}} \\ \midrule
OTU.37 & 2.68 & 7 & \mbox{\textit{Phycicola gilvus}}, \mbox{\textit{Microterricola viridarii}}, \mbox{\textit{Frigoribacterium faeni}}, \mbox{\textit{Frondihabitans sp. RS-15}}, \mbox{\textit{Frondihabitans australicus}} & 100.0 & \mbox{\textit{Actinobacteria}} \mbox{\textit{Micrococcales}} \mbox{\textit{Microbacteriaceae}} \\ \midrule
OTU.5284 & 3.56 & 7 & \mbox{\textit{Isoptericola nanjingensis}}, \mbox{\textit{Isoptericola hypogeus}}, \mbox{\textit{Isoptericola variabilis}} & 98.63 & \mbox{\textit{Actinobacteria}} \mbox{\textit{Micrococcales}} \mbox{\textit{Promicromonosporaceae}} \\ \midrule
OTU.252 & 3.34 & 7 & \mbox{\textit{Promicromonospora thailandica}} & 100.0 & \mbox{\textit{Actinobacteria}} \mbox{\textit{Micrococcales}} \mbox{\textit{Promicromonosporaceae}} \\ \midrule
OTU.244 & 3.08 & 7 & \mbox{\textit{Cellulosimicrobium funkei}}, \mbox{\textit{Cellulosimicrobium terreum}} & 100.0 & \mbox{\textit{Actinobacteria}} \mbox{\textit{Micrococcales}} \mbox{\textit{Promicromonosporaceae}} \\ \midrule
OTU.760 & 2.89 & 3 & \mbox{\textit{Dyadobacter hamtensis}} & 98.63 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Cytophagia}} \mbox{\textit{Cytophagales}} \\ \midrule
OTU.14 & 3.92 & 3 & \mbox{\textit{Flavobacterium oncorhynchi}}, \mbox{\textit{Flavobacterium glycines}}, \mbox{\textit{Flavobacterium succinicans}} & 99.09 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Flavobacteria}} \mbox{\textit{Flavobacteriales}} \\ \midrule
OTU.6203 & 3.32 & 3 & \mbox{\textit{Flavobacterium granuli}}, \mbox{\textit{Flavobacterium glaciei}} & 100.0 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Flavobacteria}} \mbox{\textit{Flavobacteriales}} \\ \midrule
OTU.159 & 3.16 & 3 & \mbox{\textit{Flavobacterium hibernum}} & 98.17 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Flavobacteria}} \mbox{\textit{Flavobacteriales}} \\ \midrule
OTU.2379 & 3.1 & 3 & \mbox{\textit{Flavobacterium pectinovorum}}, \mbox{\textit{Flavobacterium sp. CS100}} & 97.72 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Flavobacteria}} \mbox{\textit{Flavobacteriales}} \\ \midrule
OTU.131 & 3.07 & 3 & \mbox{\textit{Flavobacterium fluvii}}, \mbox{\textit{Flavobacteria bacterium HMD1033}}, \mbox{\textit{Flavobacterium sp. HMD1001}} & 100.0 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Flavobacteria}} \mbox{\textit{Flavobacteriales}} \\ \midrule
OTU.3540 & 2.52 & 3 & \mbox{\textit{Flavobacterium terrigena}} & 99.54 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Flavobacteria}} \mbox{\textit{Flavobacteriales}} \\ \midrule
OTU.107 & 2.25 & 3 & \mbox{\textit{Flavobacterium sp. 15C3}}, \mbox{\textit{Flavobacterium banpakuense}} & 99.54 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Flavobacteria}} \mbox{\textit{Flavobacteriales}} \\ \midrule
OTU.277 & 3.52 & 3 & \mbox{\textit{Solibius ginsengiterrae}} & 95.43 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Sphingobacteriia}} \mbox{\textit{Sphingobacteriales}} \\ \midrule
OTU.183 & 3.31 & 3 & {No hits of at least 90\% identity} & 89.5 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Sphingobacteriia}} \mbox{\textit{Sphingobacteriales}} \\ \midrule
OTU.5906 & 3.16 & 3 & \mbox{\textit{Terrimonas sp. M-8}} & 96.8 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Sphingobacteriia}} \mbox{\textit{Sphingobacteriales}} \\ \midrule
OTU.360 & 2.98 & 3 & \mbox{\textit{Flavisolibacter ginsengisoli}} & 95.0 & \mbox{\textit{Bacteroidetes}} \mbox{\textit{Sphingobacteriia}} \mbox{\textit{Sphingobacteriales}} \\ \midrule
OTU.369 & 5.05 & 1 & \mbox{\textit{Paenibacillus sp. D75}}, \mbox{\textit{Paenibacillus glycanilyticus}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.267 & 4.97 & 1 & \mbox{\textit{Paenibacillus pabuli}}, \mbox{\textit{Paenibacillus tundrae}}, \mbox{\textit{Paenibacillus taichungensis}}, \mbox{\textit{Paenibacillus xylanexedens}}, \mbox{\textit{Paenibacillus xylanilyticus}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.1040 & 4.78 & 1 & \mbox{\textit{Paenibacillus daejeonensis}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.57 & 4.39 & 1 & \mbox{\textit{Paenibacillus castaneae}} & 98.62 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.394 & 4.06 & 1 & \mbox{\textit{Paenibacillus pocheonensis}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.319 & 3.98 & 1 & \mbox{\textit{Paenibacillus xinjiangensis}} & 97.25 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.5603 & 3.96 & 1 & \mbox{\textit{Paenibacillus uliginis}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.1069 & 3.85 & 1 & \mbox{\textit{Paenibacillus terrigena}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.843 & 3.62 & 1 & \mbox{\textit{Paenibacillus agarexedens}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.2040 & 2.91 & 1 & \mbox{\textit{Paenibacillus pectinilyticus}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.3 & 2.61 & 1 & \mbox{\textit{[Brevibacterium] frigoritolerans}}, \mbox{\textit{Bacillus sp. LMG 20238}}, \mbox{\textit{Bacillus coahuilensis m4-4}}, \mbox{\textit{Bacillus simplex}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.335 & 2.53 & 1 & \mbox{\textit{Paenibacillus thailandensis}} & 98.17 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.3507 & 2.36 & 1 & \mbox{\textit{Bacillus spp.}} & 98.63 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.8 & 2.26 & 1 & \mbox{\textit{Bacillus niacini}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.4743 & 2.24 & 1 & \mbox{\textit{Lysinibacillus fusiformis}}, \mbox{\textit{Lysinibacillus sphaericus}} & 99.09 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.9 & 2.04 & 1 & \mbox{\textit{Bacillus megaterium}}, \mbox{\textit{Bacillus flexus}} & 100.0 & \mbox{\textit{Firmicutes}} \mbox{\textit{Bacilli}} \mbox{\textit{Bacillales}} \\ \midrule
OTU.22 & 2.8 & 7 & \mbox{\textit{Paracoccus sp. NB88}} & 99.09 & \mbox{\textit{Proteobacteria}} \mbox{\textit{Alphaproteobacteria}} \mbox{\textit{Rhodobacterales}} \\ \midrule
OTU.5 & 3.69 & 7 & \mbox{\textit{Delftia tsuruhatensis}}, \mbox{\textit{Delftia lacustris}} & 100.0 & \mbox{\textit{Proteobacteria}} \mbox{\textit{Betaproteobacteria}} \mbox{\textit{Burkholderiales}} \\ \midrule
OTU.346 & 3.44 & 3 & \mbox{\textit{Pseudoduganella violaceinigra}} & 99.54 & \mbox{\textit{Proteobacteria}} \mbox{\textit{Betaproteobacteria}} \mbox{\textit{Burkholderiales}} \\ \midrule
OTU.32 & 3.0 & 3 & \mbox{\textit{Sandaracinus amylolyticus}} & 94.98 & \mbox{\textit{Proteobacteria}} \mbox{\textit{Deltaproteobacteria}} \mbox{\textit{Myxococcales}} \\ \midrule
OTU.68 & 3.74 & 7 & \mbox{\textit{Shigella flexneri}}, \mbox{\textit{Escherichia fergusonii}}, \mbox{\textit{Escherichia coli}}, \mbox{\textit{Shigella sonnei}} & 100.0 & \mbox{\textit{Proteobacteria}} \mbox{\textit{Gammaproteobacteria}} \mbox{\textit{Enterobacteriales}} \\ \midrule
OTU.290 & 3.59 & 1 & \mbox{\textit{Pantoea spp.}}, \mbox{\textit{Kluyvera spp.}}, \mbox{\textit{Klebsiella spp.}}, \mbox{\textit{Erwinia spp.}}, \mbox{\textit{Enterobacter spp.}}, \mbox{\textit{Buttiauxella spp.}} & 100.0 & \mbox{\textit{Proteobacteria}} \mbox{\textit{Gammaproteobacteria}} \mbox{\textit{Enterobacteriales}} \\ \midrule
OTU.11 & 5.25 & 7 & \mbox{\textit{Stenotrophomonas pavanii}}, \mbox{\textit{Stenotrophomonas maltophilia}}, \mbox{\textit{Pseudomonas geniculata}} & 99.54 & \mbox{\textit{Proteobacteria}} \mbox{\textit{Gammaproteobacteria}} \mbox{\textit{Xanthomonadales}} \\ \midrule
OTU.48 & 2.99 & 1 & \mbox{\textit{Aeromonas spp.}} & 100.0 & \mbox{\textit{Proteobacteria}} \mbox{\textit{Gammaproteobacteria}} \mbox{\textit{aaa34a10}} \\ \midrule
OTU.241 & 3.38 & 3 & {No hits of at least 90\% identity} & 87.73 & \mbox{\textit{Verrucomicrobia}} \mbox{\textit{Spartobacteria}} \mbox{\textit{Chthoniobacterales}} \\ \midrule

\bottomrule
\end{longtable}

\restoregeometry
